Multi-resolution Neural Field Estimation

### 2011-03-06 Multiresolution_framework/ltx/manuscript.tex
edits to result section

\parham{Field reconstruction obtained using the state estimates of the EM algorithm at different levels of approximations separately using same observation set. (\figurename{\ref{fig:FieldEstimates}})}. \ken{Parham, can't understand the previous sentence.} The figure confirms that $j=3$ is adequate to capture the dynamics of the underlying field, where the RMSE converges to a steady value of 0.72. Fig.~\ref{fig:FieldEstimates} confirms good state estimation performance, where the estimated field is in good accordance with the true field.

>>>>

Field reconstruction at different levels of approximations shown in \figurename{\ref{fig:FieldEstimates}}. The figure confirms that $j=3$ is adequate to capture the dynamics of the underlying field, where the RMSE converges to a steady value of 0.72. Fig.~\ref{fig:FieldEstimates} confirms good state estimation performance, where the estimated field is in good accordance with the true field.
